Draft: Notes on the revised Hidden weight function

### 2024-09-25 RevisedHiddenWeight.tex
bit on AI

\begin{Prop}[Nonlinearity on the slice, adapted from~\cite{TOSC:CarMeaRot17}, Proposition 6]\label{prop:nlk}
	Let $n\in \N^*, k\in [0,n]$, for every $n$-variable Boolean function $f$ over $\Ekn{k}{n}$:
	\[ \NLk{k}(f)=\frac{|\Ekn{k}{n}|}{2} -\frac{\max_{a\in \F_2^n} |\wtk{f}{k}(a)|}{2}  .\]
\end{Prop}

@@

\begin{Prop}[Weightwise restricted Walsh transform and addition of symmetric function (~\cite{INDO:GinMea22}, Proposition $4$)]\label{prop:AddSym}
	Let $n\in \N^*$, $k\in [0,n]$ and $f \in \Bn{n}$, the following holds on $f+\phikn{k}{n}$
	\[\forall a\in \F_2^n, \forall i\in [0,n]\setminus \{k\}, \wtk{f+\phikn{k}{n}}{i}(a)=\wtk{f}{i}(a),\text{ and } \wtk{f+\phikn{k}{n}}{k}(a)=-\wtk{f}{i}(a).\]	
\end{Prop}

@@

\pmnote{Bounds on Dnk from complex analysis}

\pmnote{practical experiments for the function.}

@@

>>>>

@@

@@

@@

\subsection{Algebraic immunity of $f$}

\begin{proposition}[Algebraic immunity of $f$]
	Let $n\in \N$ be even, $f$ defined as
	$f(x_1,\cdots,x_n)=\left(\sum_{i=1}^{n/2} (x_i+1) x_{i+\frac{n}{2}}\right) + \sum_{k=1}^n \phikn{k}{n} x_k$ and $h$ denote the $n$-variable HWBF, the following holds:
	\[\AI(f)\ge \AI(h)-2.\]
\end{proposition}
\begin{proof}
	content...
\end{proof}
